---
title: "lab_report_knapsack"
author: "Zhendong Wang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab_report_knapsack}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


## knapsack_brute_force() Function

The codes below shows the `knapsack_brute_force()` function result and how many time did it take for the computation of 16 observations.

```{r, fig.show='hold'}
my_df <- Lab6::knapsack_objects
start.time<-Sys.time()
Lab6::knapsack_brute_force(x=my_df[1:16,],W=3500)
end.time<-Sys.time()
time.taken <- end.time - start.time
time.taken
```



## knapsack_dynamic() Function

The codes below shows the `knapsack_dynamic()` function result and how many time did it take for the computation of 500 observations.

```{r}
start.time<-Sys.time()
Lab6::knapsack_dynamic(x=my_df[1:500,],W=3500)
end.time<-Sys.time()
time.taken <- end.time - start.time
time.taken
```

## knapsack_greedy() Funciton

The codes below shows the `knapsack_greedy()` function result and how many time did it take for the computation of 1,000,000 observations.

```{r}
start.time<-Sys.time()
Lab6::knapsack_dynamic(x=my_df[1:1000000,],W=3500)
end.time<-Sys.time()
time.taken <- end.time - start.time
time.taken
```


