---
title: "lab_report_knapsack"
author: "Zhendong Wang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab_report_knapsack}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## The Knapsack Package

The package contains three different functions for solving what is called the knapsack problem. They are using diverse Big Oh notations to work out this problem. Below there will be the examples about the three functions below.

## Data

At first it need to create a data set to generate these data for the calculation later, as we need 1,000,000 observations to be analysed in the `knapsack_greedy()` part, so the number was changed `n=1000000` in the data set. Here we can show some of the data, the 1,000,000 items each contain an unique weight "w"" and a value "v".

```{r}
library(Lab6)
head(Lab6::knapsack_objects)
```


## knapsack_brute_force() Function
 
The codes below shows the `knapsack_brute_force()` function result and how many time did it take for the computation of 16 observations.

```{r, fig.show='hold'}
my_df <- Lab6::knapsack_objects
start.time<-Sys.time()
Lab6::knapsack_brute_force(x=my_df[1:16,],W=3500)
end.time<-Sys.time()
time.taken <- end.time - start.time
time.taken
```



## knapsack_dynamic() Function

The codes below shows the `knapsack_dynamic()` function result and how many time did it take for the computation of 500 observations.

```{r}
start.time<-Sys.time()
Lab6::knapsack_dynamic(x=my_df[1:500,],W=3500)
end.time<-Sys.time()
time.taken <- end.time - start.time
time.taken
```

## knapsack_greedy() Funciton

The codes below shows the `knapsack_greedy()` function result and how many time did it take for the computation of 1,000,000 observations.

```{r}
start.time<-Sys.time()
invisible.output <- Lab6::knapsack_greedy(x=my_df[1:1000000,],W=3500)
end.time<-Sys.time()
time.taken <- end.time - start.time
time.taken
```

## Profiling the code

"Question:How large performance gain could you get by using Rcpp and C++?"

## Rcpp

"Question How large performance gain could you get by parallelizing brute force search?"