---
title: "Lab 4"
author: "Rasmus Holm"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Lab4}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```
# Linear Regression Test

## Loading the data set
We will use the iris data set to perform our testing which is a famous data set containing information about flowers.

```{r}
library(Lab4)
library(datasets)

data <- datasets::iris
```

## Perform linear regression
In order to perform linear regression, we use the linreg function which takes a formula describing the model and a data frame.

```{r}
model <- linreg(formula = Petal.Length ~ Species, data=data)
```

The returning object is a Reference Class of type "LinearRegressionModel" that contains all the information about the linear model. It provides methods to investigate the model and its parameters.

```{r}
# Shows the coefficients that were estimated
model$coef()
# Shows the residuals.
head(model$resid())
# Shows the fitted values.
head(model$pred())
```

The class object also have methods to show detailed view of the model.
```{r}
# Shows how the linreg function was called and the coefficients.
model$print()
# Shows a detailed summary of the residuals and coefficients with related statistics.
model$summary()
```

To get a better understanding to whether the model is linear or not, the model has a method for plotting "fitted vs residuals" and "scale-location" plots. Go [here](http://data.library.virginia.edu/diagnostic-plots) for more information about the plots.

```{r, fig.show='hold', fig.width=6, fig.height=5, fig.align='center'}
model$plot()
```
